State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2015-12-28 draft.tex
Up to remark 14

@@

\emph{Notation:} Throughout this paper we denote 
the image of a set $\mathcal C\subseteq X$ under the map $f:X\mapsto Y$ as $f\vert_{\mathcal C} = \{y\in Y:\exists x\in\mathcal C,\;y=f(x)\}$. 
%
Given a collection of row-vectors $a_i$ and scalars $b_i$ for $i\in\{1,\ldots,m\}$, we denote as ${\bf{a}}_{\mathcal I}$ and
${\bf{b}}_{\mathcal I}$ the matrix and vector, respectively, with rows $a_i$ and $b_i$ for all indices $i$ in the index set $\mathcal I\subseteq\{1,\dots,m\}$.

@@

with $J(x,u,w) = \frac{1}{2}\left(x^T Qx + u^TRu - \gamma^2 w^T w\right)$,

@@

We assume that $Q\geq0$ and $R>0$ are semi-positive and positive definite constant matrices respectively,
the matrices $A,B,D$ are also assumed to be deterministic and known.
Since we require guarantees of stability and feasibility in presence of disturbances arbitrary state constraints
like~\eqref{eq:general:state:constraints} can not be robustly satisfied~\cite{Bertsekas:1971}, instead specially designed
ones are used.

@@

\emph{maximal robust positive invariant} (MRPI) set~$\mathcal X^\infty\subseteq\mathcal X$ 

@@

Starting from the MRPI set~$\mathcal X_0=\mathcal X^\infty$ we recursively define

@@

  \mathcal X_i = \{x:\exists u\in U\; (x,u)\in\mathcal Z_i\}.

@@

controller~$K$ as the optimal unconstrained solution to~\eqref{seq:general:problem:statement}, i.e. they satisfy
$J_0^\ast(x) - J_0^\ast(x^+)\geq J(x,Kx,w)$, see e.g.~\cite{Boyd:94}.
Both input and state constraint sets are assumed polyhedral $U=\{u:F_iu\leq1\forall i\in\mathcal I_U\}$ and $\mathcal X = 
\{x:\genmat_i x\leq \genvec_i\forall i\in\mathcal I_{\mathcal X}\}$.

@@

  \mathcal W(x,u) = \{w:G_i w\leq\max_{k}\{H_{i,k}^x x + H_{i,k}^u + h_{i,k}\}\forall i\in\mathcal I_{\mathcal W}\}.

@@

In this section we discuss \emph{parametric convexity}, an attribute of sets valued maps 
(so called point-to-set maps, see e.g.~\cite{Hogan:1973}) we exploit later on to prove 
convexity of a generalised Pontryagin difference in order to 

@@

  Let $X\subseteq\mathbb R^d, Y\subseteq\mathbb R^n$, let $\mathscr P(Y)$ 
  denote the power set of $Y$, 
  and $\mathcal W:X\rightarrow \mathscr P(Y)$, $X\ni p\mapsto \mathcal W(p)
  \subset Y$ be a continuous point-to-set map. The map $\mathcal W$ is called 
  \emph{parametrically convex} if it satisfies

@@

  for all $p_1,p_2\in X$ and $\lambda\in[0,1]$.

@@

Notice that Definition~\ref{def:parametric:convexity} does not require convexity of~$\mathcal W(p)$ for all
$p\in X$, we will however only treat maps~$\mathcal W$ for which $\mathcal W(p)$ is convex.

\subsection{Properties of Parametrically Convex Maps}\label{ssec:properties:of:p:convex:maps}
In this subsection we introduce an equivalent characterisation of parametric 
convexity that will yield some insight on the topological 
definition~\ref{def:parametric:convexity}, for this we characterise parametric
convexity in terms of the graph of the point-to-set map.
\begin{defi}\label{def:graph:of:map}
Let $\mathcal W:X\rightarrow \mathscr P(Y)$ be a continuous point-to-set map
such that $\mathcal W(p)$ is convex for all $p\in X$, then 
  \mathscr G(\mathcal W) = \{(p,x) \in\mathbb R^{d+n}: x\in\mathcal W(p)\},
denotes the \emph{graph} of $\mathcal W$,
  \text{int}(\mathscr G(\mathcal W)) = \{(p,x) \in\mathbb R^{d+n}: \forall d\in\mathbb R^n\;\exists 
  \epsilon>0 : x+\epsilon d\in \mathcal W(p)\}
its \emph{interior} and
  \partial \mathscr G(\mathcal W) = \mathscr G(\mathcal W)\setminus \textup{int}(\mathscr G(\mathcal W))
its \emph{boundary}. 
The \emph{orientation cone} for all $(p,x)\in\partial\mathscr G(\mathcal W)$
is given by
  \mathcal N\mathcal W(p,x) = \{d\in\mathbb R^n: x+\epsilon d \not\in \mathcal W(p)\; \forall \epsilon>0\}.

@@

Notice, that definition~\ref{def:graph:of:map} is given in terms of the \emph{set variable} $x$ rather than \emph{graph variable} $(p,x)$.
Furthermore, notice that the orientation cone contains all directions that 
point out of the set, hence all linear combinations thereof.

@@

We state the central theorem to connect parametric convexity of a set valued 
map $\mathcal W$ with properties of its graph $\mathscr G(\mathcal W)$.
\begin{thm}\label{thm:p:convexity:graph}
The map $\mathcal W$ is parametrically convex iff for all $(p_1,x_1),(p_2,x_2)\in\partial\mathscr G(\mathcal W)$
with $\mathcal N\mathcal W(p_1,x_1)\cap\mathcal N\mathcal W(p_2,x_2)\neq\emptyset$ and $p_1\neq p_2$ 
\begin{equation}\label{eq:graph:def:p:convexity}
\lambda (p_1,x_1) + (1-\lambda) (p_2,x_2) \not\in\textup{int} (\mathscr G(\mathcal W))
holds for all $\lambda\in(0,1)$.

@@

Assume~\eqref{eq:graph:def:p:convexity} holds for $(p_1,x_1),(p_2,x_2)\in\partial\mathscr G(\mathcal W)$.
Then the Minkowski functional (see e.g.~\cite{Rudin:91}) yields $\mu_{\mathscr G(\mathcal W)}(\mathcal W(\lambda p_1 + (1-\lambda)p_2),
\lambda x_1+(1-\lambda)x_2)\geq1$,
i.e. all interpolation points lie either on the boundary or outside the set $\mathcal W(\lambda p_1+(1-\lambda)p_2)$
therefore the set of all possible interpolation points 
  \lambda \mathcal W(p_1)\oplus (1-\lambda)\mathcal W(p_2) = \{x:x=\lambda x_1 + (1-\lambda) x_2 \wedge\\ x_1\in\mathcal 
  W(p_1) \wedge x_2\in\mathcal W(p_2)\}
contains the set $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$.
Now assume $\mathcal W$ is parametrically convex but~\eqref{eq:graph:def:p:convexity} is not satisfied for 
N\mathcal W(p_2,x_2)\neq\emptyset$, i.e. $\lambda x_1 + (1-\lambda)x_2\in\text{int}(\mathcal W(\lambda p_1 + 
(1-\lambda)p_2)$.
This implies that a full dimensional ball $B_\epsilon(x ) = \{y:\| 
x-y\|<\epsilon\}$
is contained in $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$, i.e. $B_\epsilon(\lambda x_1 + (1-\lambda)x_2 )\subset
\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for some $\epsilon>0$.
Since $\mathcal N\mathcal W(p_1,x_1)\cap\mathcal N\mathcal W(p_2,x_2)\neq\emptyset$, there exist directions 
$d\in\mathcal N\mathcal W(p_1,x_1)\cap\mathcal N\mathcal W(p_2,x_2)$ which can not be represented as $d=\lambda d_1+
(1-\lambda)d_2$ with $x_1 + \epsilon d_1\in\mathcal W(p_1)$ and $x_2  + \epsilon d_2\in\mathcal W(p_2)$, however since $B_\epsilon$ is full dimensional
all directions exist, $x+\epsilon d\in\mathcal W(\lambda p_1 + (1-\lambda)p_2)$.
Hence, $\mathcal W$ can not be parametrically convex.

@@

Notice that condition~\eqref{eq:graph:def:p:convexity} is a non-convexity condition on the graph $\mathscr G(\mathcal W)$.
If $\mathscr G(\mathcal W)$ is strictly convex anywhere~\eqref{eq:graph:def:p:convexity} is violated and 
$\mathcal W$ can not be parametrically convex.
map with a continuous function 
$r: \mathbb R^d \times\mathbb R^n \rightarrow \mathbb R,(p,x)\mapsto r(p,x)$, 
convex iff the function $r$ is concave in $p\in\mathbb R^d$ and convex in $x\in
\mathbb R^n$.
The convexity in $x\in\mathbb R^n$ is required to satisfy the requirement that $\mathcal W(p)$ is convex
for all fixed values of $p\in\mathbb R^d$. 
Assume that for some region $\Omega\subset\mathbb R^d$ the function $r(\cdot,x)$ is non-concave (i.e. 
strictly convex), any convex subset $\mathcal C\subseteq\Omega$ will hence be such that $\mathscr 
In particular all lines between all $(p_1,x_1),(p_2,x_2)\in \partial\mathscr G(\mathcal W)\vert_{\mathcal C}$ will satisfy
$\lambda (p_1,x_1) + (1-\lambda) (p_2,x_2) \in\textup{int} (\mathscr G(\mathcal W))\vert_{\mathcal C}$ since
This implies that $r(\cdot,x)$ can not be non-concave in any non-trivial set $\Omega\subseteq\mathbb R^d$ and still
be parametrically convex.

@@

The polytopic parametric set valued map $\mathcal W(p):=\{x: a_i x + b_i p\leq c_i \forall i\leq m\}$ is not parametrically convex for 
any non-trivial matrix $B$.

@@

	\mathscr G(\mathcal W) = \{(p,x):a_i x + b_i p\leq c_i \forall i\leq m\}

@@

  \mathcal W(p) := \left\{x: a_i x \leq \max_{k\leq l}\{b_{i,k} + c_{i,k}p\},i\leq m\right\}
is parametrically convex iff the number of vertices $v_\kappa(p)$ and rays $r_\eta(p)$ is constant.

@@

\item Notice that $h_i(p) = \max_{k\leq l} \{b_{i,k} + c_{i,k}p\}$ is a multi-parametric linear program (mpLP),
its solution is a piecewise affine function $h_i(p) = b_{i,k^\ast_i} + c_{i,k^\ast_i}p$ where $k^\ast_i(p)$ is constant
inside a polytopic complex, see e.g.~\cite{spjotvold:2005}.
That means that there exists a finite polyhedral partitioning $\mathbb R^d = \bigcup_{j\leq t} \mathcal P_j$ with convex polyhedra 
$\mathcal P_j$ such that ${\bf{k}}^\ast\vert_{\mathcal P_j} = (k_1^\ast,\dots,k_m^\ast) = const$.
A standard degeneracy assumption is that in neighbouring partitions ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$ and 
${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ differ in exactly one element.
This partitioning implies that the graph $\mathscr G(\mathcal W)$ is given as a finite union of polyhedra

@@

  \mathscr G(\mathcal W) = \bigcup_{j\leq t} \left\{x: a_i x \leq b_{i,k_i^\ast} + c_{i,k_i^\ast}p,i\leq m
  \right\}\bigr\vert_{\mathcal P_{j}}

@@

But this implies that if the number of vertices or rays changes inside any partition $\mathcal P_j$ then $\mathscr
G(\mathcal W)\vert_{\mathcal P_j}$ is a strictly convex polyhedron and corollary~\ref{thm:polytopic:set:not:p:convex} applies.
\item Our attention hence is concentrated to the boundaries of the partitions $\mathcal P_j$.
These are the points $\mathcal P_{j_1} \cap \mathcal P_{j_2}$ where some mpLP changes its solution, i.e. 

@@

Notice that a vertex $v_\kappa(p)$ is given by \emph{active} and \emph{inactive} inequalities, i.e. $\mathcal A_\kappa(p)$ and
$\mathcal I_\kappa(p) = \{1,\dots,m\}\setminus\mathcal A_\kappa(p)$ respectively.

@@

  a_i v_\kappa(p) &< b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\mathcal I_\kappa(p)

@@

In order for the number of vertices to change, there must be a hyperplane $fp=g$, such that the number of vertices for $fp<g$ is 

@@

For vertices $v_{\kappa_1}(p)$ and $v_{\kappa_2}(p)$ to merge the index sets $\mathcal A_{\kappa_1}(p)$ and 
$\mathcal A_{\kappa_2}(p)$ have to differ in only one 
element, i.e. $\mathcal A_{\kappa_1}(p) = \mathcal J\cup \{s\}$ and $\mathcal A_{\kappa_2}(p) = \mathcal J\cup\{u\}$ for $fp>g$.
Furthermore, for $p$ with $fp\leq g$ we have $v_{\kappa_1}(p)=v_{\kappa_2}(p)$, this implies $\mathcal A_{\kappa_1}(p) = 

@@

Since only one alteration of the active index set is considered (due to non-degeneracy assumptions), the active set 

@@

Hence on the hyperplane $fp=g$ both, the maximising index ${\bf{k}}^\ast(p)$ and the active index sets $\mathcal A_{\kappa_1}(p)$ 
and $\mathcal A_{\kappa_2}(p)$ change, which is means the problem is degenerate.
\item In order for the degenerate graph $\mathscr G(\mathcal W)$ to be parametrically convex the overdetermined 
vertex $v_{\kappa_1}(p)=v_{\kappa_2}(p)$ have to be identical, in particular their dependence on $p$ has to be identical.
This can be expressed with the implicit function theorem:

@@

which leads to 

@@

  {\bf{c}}_{\mathcal J\cup \{u\}} \frac{dv_{\kappa}}{dp} &= {\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
since we can assume that the inequalities are non-redundant for some right hand side, we obtain that 

@@

Notice that~\eqref{eq:derivative:condition:on:index:sets} is again a degenerate condition, since arbitrarily small perturbations
will produce different behaviour.

@@

@@

Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} is essential for numerical evaluation, as it can be reformulated to:
The set valued map defined by~\eqref{eq:definition:PWA:polytopic:set:general} is non-degenerate and parametrically convex iff 
it has a constant number of vertices throughout the parameter space~$X$.

@@

In order to determine MRPI sets we need to be able to calculate the Pontryagin difference between sets, hence we introduce
the following.

@@

  Let $S\subseteq X$ be a convex set and let $\mathcal W:X\rightarrow\mathscr P(X)$ be a parametrically convex point-to-set
  map such that $\mathcal W(p)$ is convex for all $p\in X$, then $S\ominus \mathcal W(S)$ is convex.

@@

@@

To prove the convexity of $ Z :=  S\ominus \mathcal W( S)$ we pick any $z_1,z_2\in Z$, then
by definition of the parametric Pontryagin difference, we have

@@

  \{z_i\} \oplus \mathcal W(z_i) \subseteq S,\; i=1,2.
To see that $ Z$ is convex we show that line segments between
all possible $z_1$ and $z_2$ are subsets of $ Z$, i.e.~for all $\lambda \in [0,1]$,
\begin{aligned}

@@

  \subseteq &\lambda\underbrace{(\{z_1\}\oplus \mathcal W(z_1))}_{\subseteq S}\oplus

>>>>

\newcommand{\todo}[1]{\textcolor{blue}{#1}}
\newcommand{\highlight}[1]{\textcolor{red}{#1}}

@@

\emph{Notation:} Throughout this paper 
%
we denote sequences of integers $\mathbb N_m = \{1,\ldots,m\}$ for $m\geq 1$ and $\mathbb N_{[n,m]} = \{n,\ldots,m\}$ for $n\leq m$.
%
Given a collection of row-vectors $a_i$ and scalars $b_i$ for $i\in\mathbb N_m$, we denote as ${\bf{a}}_{\mathcal I}$ and ${\bf{b}}_{\mathcal I}$ the matrix and vector, respectively, with rows $a_i$ and $b_i$ for all indices $i$ in the index set $\mathcal I\subseteq \mathbb N_m$.
%
We denote 
the image of a set $\mathcal C\subseteq X$ under the map $f:X\mapsto Y$ as $f\vert_{\mathcal C} = \{y\in Y:\exists x\in\mathcal C,\;y=f(x)\}$. 
%
For $x\in\mathbb R^n$ the Euclidean norm is denoted $\|x\|=\sqrt{x^T x}$, and we define the weighted norm $\|x\|_P=\sqrt{x^T P x}$ for a positive definite matrix $P\in\mathbb R^{n\times n}$, and for any $\epsilon > 0$ we define the ball $B_\epsilon(x) = \{y\in\mathbb R^n : \|x-y\| \leq \epsilon\}$.

@@

with $J(x,u,w) = \frac{1}{2}(\|x\|_Q^2 + \|u\|_R^2 - \gamma^2 \|w\|^2)$,

@@

We assume that $Q$ and $R$ are, respectively, semi-positive definite and positive definite constant matrices, the matrices $A,B,D$ are also assumed to be deterministic and known.
\todo{Since we require guarantees of stability and feasibility in presence of disturbances arbitrary state constraints
like~\eqref{eq:general:state:constraints} cannot be robustly satisfied~\cite{Bertsekas:1971}, instead specially designed
ones are used.}

@@

\emph{maximal robust positively invariant} (MRPI) set~$\mathcal X^\infty\subseteq\mathcal X$ 

@@

Starting from the MRPI set~$\mathcal X_0=\mathcal X^\infty$ we define, for $i\in\mathbb N_\infty$,
%$i=1,2,\ldots$,  

@@

  \mathcal X_i = \{x:\exists u\in U, \; (x,u)\in\mathcal Z_i\}.

@@

controller~$K$ as the optimal unconstrained solution to~\eqref{seq:general:problem:statement}, i.e.\ they satisfy
$J_0^\ast(x) - J_0^\ast(x^+)\geq J(x,Kx,w)$ for all $w$; see e.g.~\cite{Boyd:94} for details of how to compute $P_0$ using semidefinite programming.
Both input and state constraint sets are assumed polyhedral $U=\{u:F_iu\leq1\; \forall i\in\mathbb N_{n_u}\}$ and $\mathcal X = 
\{x:\genmat_i x\leq \genvec_i\; \forall i\in\mathbb N_{n_x}\}$.

@@

  \mathcal W(x,u) = \bigl\{w:G_i w\leq\max_{k}\{H_{i,k}^x x + H_{i,k}^u + h_{i,k}\}\; \forall i\in\mathbb N_{n_w}\bigr\}.

@@

This section defines and discusses the property of \emph{parametric convexity} in the context of set valued maps (so called point-to-set maps, see e.g.~\cite{Hogan:1973}). We use this property 
%here and in Section~\ref{sec:example:I} 
to demonstrate the convexity of a generalised Pontryagin difference and thus determine the conditions under which $\mathcal{X}^\infty$ and $\mathcal{X}_i$ are convex polyhedra. 
Throughout this section we refer to sets $X\subseteq\mathbb R^d$ and $Y\subseteq\mathbb R^n$, and we denote the power set of $Y$ as $\mathscr P(Y)$.

@@

%Let $X\subseteq\mathbb R^d, Y\subseteq\mathbb R^n$, let $\mathscr P(Y)$ denote the power set of $Y$, and
Let $\mathcal W:X\rightarrow \mathscr P(Y)$, where $X\ni p\mapsto \mathcal W(p) \subset Y$, be a continuous point-to-set map. The map $\mathcal W$ is called \emph{parametrically convex} if it satisfies

@@

  for all $p_1,p_2\in X$ and $\lambda\in (0,1)$.

@@

Notice that Definition~\ref{def:parametric:convexity} does not require convexity of~$\mathcal W(p)$. However, we will only consider maps~$\mathcal W$ for which $\mathcal W(p)$ is convex for all $p\in X$.

\subsection{Properties of Parametrically Convex Maps}\label{ssec:properties:of:p:convex:maps}
%
We begin by introducing an equivalent characterisation of parametric convexity that provides an insight into the geometrical properties of 
point-to-set maps satisfying~(\ref{eq:def:parametrically:convex}).
%Definition~\ref{def:parametric:convexity}. 
This is based on a description of parametric convexity in terms of conditions on the graph of a point-to-set map.
%
\begin{defi}\label{def:graph:of:map}
Let $\mathcal W:X\rightarrow \mathscr P(Y)$ be a continuous point-to-set map
such that $\mathcal W(p)$ is convex for all $p\in X$, then 
%
\[
  \mathscr G(\mathcal W) = \{(p,x) \in\mathbb R^{d+n}: x\in\mathcal W(p)\}
\]
%
denotes the \emph{graph} of $\mathcal W$,
%
\[
  \text{int}(\mathscr G(\mathcal W)) = \{(p,x) \in\mathbb R^{d+n}: \forall \xi\in\mathbb R^n\;\exists 
  \epsilon>0 : x+\epsilon \xi\in \mathcal W(p)\}
\]
%
is its \emph{interior}, and
%
\[
  \partial \mathscr G(\mathcal W) = \mathscr G(\mathcal W)\setminus \textup{int}(\mathscr G(\mathcal W))
\]
%
denotes its \emph{boundary};
%
furthermore for any $(p,x)\in\partial\mathscr G(\mathcal W)$ the \emph{orientation cone} is defined as 
%
\[
  \mathcal N\mathcal W(p,x) = \{\xi\in\mathbb R^n: x+\epsilon \xi \not\in \mathcal W(p)\; \forall \epsilon>0\} .
\]
%for all $(p,x)\in\partial\mathscr G(\mathcal W)$.

\end{defi}
%
\begin{rem}
%
Note that the orientation cone is defined in the space of the
\emph{set variable} $x$ rather than \emph{graph variable} $(p,x)$.
%
Furthermore, the orientation cone contains all directions that 
point out of the set $\mathcal W(p)$ and hence all linear combinations thereof.
%
\end{rem}
%
The central idea connecting parametric convexity of a set valued map $\mathcal W$ with properties of its graph $\mathscr G(\mathcal W)$ is stated next.
%
\begin{thm}\label{thm:p:convexity:graph}
The map $\mathcal W$ is parametrically convex iff for all $(p_1,x_1), (p_2,x_2)\in\partial\mathscr G(\mathcal W)$
with $p_1\neq p_2$ and $\mathcal N\mathcal W(p_1,x_1)\cap\mathcal N\mathcal W(p_2,x_2)\neq\emptyset$,
%
\begin{equation}\label{eq:graph:def:p:convexity}
\lambda (p_1,x_1) + (1-\lambda) (p_2,x_2) \not\in\textup{int} (\mathscr G(\mathcal W))
\end{equation}
%
holds for all $\lambda\in(0,1)$.
%
\end{thm}
%
\begin{proof}
%
Assume~\eqref{eq:graph:def:p:convexity} holds for $(p_1,x_1),(p_2,x_2)\in\partial\mathscr G(\mathcal W)$.
%
Then the extension of the definition of the Minkowski functional (see e.g.~\cite{Rudin:91}) to the graph $\mathscr G(\mathcal W)$,
\[
\mu_{\mathscr G(\mathcal W)} \bigl(
\mathcal W(p), x \bigr)
:= \min_\mu \{\mu \geq 0 : x \in \mu \mathcal W(p)\},
\]
%Then the Minkowski functional (see e.g.~\cite{Rudin:91}) yields $\mu_{\mathscr G(\mathcal W)}(\lambda p_1 + (1-\lambda)p_2,\lambda x_1+(1-\lambda)x_2)\geq1$,
yields $\mu_{\mathscr G(\mathcal W)}\left(\mathcal W(\lambda p_1 + (1-\lambda)p_2),\lambda x_1+(1-\lambda)x_2\right)\geq1$ for all $\lambda\in(0,1)$. Therefore $\lambda x_1 + (1-\lambda) x_2$
lies either outside the set $\mathcal W(\lambda p_1+(1-\lambda)p_2)$ or on its boundary for all $\lambda\in(0,1)$, and hence the set of all possible interpolation points 
%
\[
\begin{split}
  \lambda \mathcal W(p_1)\oplus (1-\lambda)\mathcal W(p_2) = \{&x:x=\lambda x_1 + (1-\lambda) x_2 \wedge\\ &x_1\in\mathcal 
  W(p_1) \wedge x_2\in\mathcal W(p_2)\}
\end{split}
\]
%
contains the set $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for all $\lambda\in(0,1)$.
%

Now suppose that $\mathcal W$ is parametrically convex and that~\eqref{eq:graph:def:p:convexity} is not satisfied for 
N\mathcal W(p_2,x_2)\neq\emptyset$, 
%i.e.~that for some $\lambda \in (0,1)$
% \[
% \lambda x_1 + (1-\lambda)x_2\in\text{int}(\mathcal W(\lambda p_1 + 
% (1-\lambda)p_2) ,
% \]
i.e.~that there exists $\epsilon>0$ such that the ball
%full dimensional ball 
%$B_\epsilon(x ) = \{y:\| x-y\|<\epsilon\}$
$B_\epsilon(\lambda x_1 + (1-\lambda)x_2 )$
is contained in $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for some $\lambda \in (0,1)$.
%i.e. $B_\epsilon(\lambda x_1 + (1-\lambda)x_2 )\subset \mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for some $\epsilon>0$.
But this implies that $\lambda x_1 + (1-\lambda) x_2 + \epsilon\xi \in \mathcal W(\lambda p_1+(1-\lambda)p_2)$  for all $\xi\in\mathbb R^n$ such that $\|\xi\| = 1$, whereas
$\mathcal N\mathcal W(p_1,x_1)\cap\mathcal N\mathcal W(p_2,x_2)\neq\emptyset$ implies that there exist directions 
$\xi\in\mathcal N\mathcal W(p_1,x_1)\cap\mathcal N\mathcal W(p_2,x_2)$ which cannot be represented as
% a convex combination, 
$\xi=\lambda \xi_1+
(1-\lambda)\xi_2$
with
%, of $\xi_1$ and $\xi_2$ such that 
$x_1 + \epsilon \xi_1\in\mathcal W(p_1)$ and $x_2  + \epsilon \xi_2\in\mathcal W(p_2)$.
%however since $B_\epsilon$ is full dimensional
%all directions exist, $x+\epsilon \xi\in\mathcal W(\lambda p_1 + (1-\lambda)p_2)$.
It follows that $\mathcal W$ cannot be parametrically convex in this case.

@@

Condition~\eqref{eq:graph:def:p:convexity} requires that the graph $\mathscr G(\mathcal W)$ is non-convex.
Indeed if $\mathscr G(\mathcal W)$ is strictly convex at any $(p,x)\in\partial \mathscr G (\mathcal W)$, then~\eqref{eq:graph:def:p:convexity} is violated and 
$\mathcal W$ cannot be parametrically convex.

@@

map where 
$r: \mathbb R^d \times\mathbb R^n \rightarrow \mathbb R$, $(p,x)\mapsto r(p,x)$ is a continuous function which is convex in $x \in\mathbb R^n$, 
%$r: \mathbb R^d \times\mathbb R^n \ni (p,x) \mapsto r(p,x) \in \mathbb R$ is  a continuous function, 
convex iff the function $r$ is concave in $p\in\mathbb R^d$.

@@

Convexity of $r(p,x)$ in $x\in\mathbb R^n$ is assumed so that $\mathcal W(p)$ is a convex set for all fixed values of $p\in\mathbb R^d$.
Suppose that, for given $x\in\mathbb R^n$, $r(p,x)$ is non-concave (i.e. 
strictly convex) in $p$, for all $p$ in some region $\Omega\subset\mathbb R^d$. 
%Suppose that for some region $\Omega\subset\mathbb R^d$ the function $r(\cdot,x)$ is non-concave (i.e. strictly convex), 
Then any convex subset $\mathcal C\subseteq\Omega$ will be such that $\mathscr 
Furthermore, for any $(p_1,x_1),(p_2,x_2)\in \partial\mathscr G(\mathcal W)\vert_{\mathcal C}$ we have
$\lambda (p_1,x_1) + (1-\lambda) (p_2,x_2) \in\mathrm{int} (\mathscr G(\mathcal W))\vert_{\mathcal C}$ for all $\lambda\in(0,1)$ since
Hence~\eqref{eq:graph:def:p:convexity} is violated in this case, implying that $r(\cdot,x)$ cannot be non-concave on any non-trivial set $\Omega\subseteq\mathbb R^d$ if $\mathcal W$ is parametrically convex. 
Conversely, if $r(p,x)$ is concave in $p$ for all $p\in\mathbb R^d$, then the conditions of Theorem~\ref{thm:p:convexity:graph} necessarily hold.
%then~\eqref{eq:graph:def:p:convexity} necessarily holds.

@@

@@

The polytopic parametric set valued map $\mathcal W(p):=\{x: a_i x + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
%i\leq m\}$ 
is not parametrically convex for 
any non-trivial matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$.

@@

	\mathscr G(\mathcal W) = \{(p,x):a_i x + b_i p\leq c_i \; \forall i\in\mathbb N_m\}

@@

  \mathcal W(p) := \left\{x: a_i x \leq \max_{k\in\mathbb N_l}\{b_{i,k} + c_{i,k}p\} \; \forall i\in\mathbb N_m \right\}
is parametrically convex iff the number of vertices, $v_\kappa(p)$, and rays, $r_\eta(p)$, of $\mathcal W(p)$ is independent of $p$.

@@

\item Note that $h_i(p) = \max_{k\in\mathbb N_l} \{b_{i,k} + c_{i,k}p\}$ is a multi-parametric linear program (mpLP),
the solution of which is a piecewise affine function $h_i(p) = b_{i,k^\ast_i} + c_{i,k^\ast_i}p$, where $k^\ast_i(p)$ is piecewise constant on a polytopic complex (see e.g.~\cite{spjotvold:2005}).
This means that there exists a finite partition 
of $\mathbb R^d$ 
% = \bigcup_{j\leq t} \mathcal P_j$
into convex polyhedra 
$\mathcal P_j$ such that $\bigcup_{j\in\mathbb N_t} \mathcal P_j = \mathbb R^d$ and 
${\bf{k}}^\ast(p) = (k_1^\ast(p),\dots,k_m^\ast(p))$ is constant for all $p \in \mathcal P_j$.
% A standard degeneracy assumption is that in neighbouring partitions ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$ and 
% ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ differ by exactly one element.
Hence the graph $\mathscr G(\mathcal W)$ is given by a finite union of polyhedra

@@

  \mathscr G(\mathcal W) = \bigcup_{j\in\mathbb N_t} \left\{x: a_i x \leq b_{i,k_i^\ast} + c_{i,k_i^\ast}p \; \forall i \in\mathbb N_m \right\}\bigr\vert_{\mathcal P_{j}}

@@

and it follows that if the number of vertices or rays changes within any partition $\mathcal P_j$ then $\mathscr
G(\mathcal W)\vert_{\mathcal P_j}$ is a strictly convex polyhedron and Corollary~\ref{thm:polytopic:set:not:p:convex} applies.
\item Our attention is therefore concentrated on the boundaries of partitions $\mathcal P_j$, at points $p\in\mathcal P_{j_1} \cap \mathcal P_{j_2}$ where 
%some mpLP changes its solution, i.e. 

@@

Notice that a vertex $v_\kappa(p)$ is defined by \emph{active} and \emph{inactive} inequalities, namely $\mathcal A_\kappa(p)$ and
$\mathcal I_\kappa(p) = \mathbb N_m
%\{1,\dots,m\}
\setminus\mathcal A_\kappa(p)$ respectively, where

@@

  a_i v_\kappa(p) &< b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\mathcal I_\kappa(p) .

@@

A standard degeneracy assumption is that in neighbouring partitions ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$
and ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ differ by exactly one element.
Hence, in order for the number of vertices to change, there must be a hyperplane $fp=g$, such that the number of vertices for $fp \leq g$ is 

@@

In order for vertices $v_{\kappa_1}(p)$ and $v_{\kappa_2}(p)$ to merge, the index sets $\mathcal A_{\kappa_1}(p)$ and 
$\mathcal A_{\kappa_2}(p)$ have to differ by only one 
element, i.e.\ $\mathcal A_{\kappa_1}(p) = \mathcal J\cup \{s\}$ and $\mathcal A_{\kappa_2}(p) = \mathcal J\cup\{u\}$ if $fp>g$.
Furthermore, for $p$ such that $fp\leq g$ we have $v_{\kappa_1}(p)=v_{\kappa_2}(p)$, implying that $\mathcal A_{\kappa_1}(p) = 

@@

Since only one change in the active index set is considered (due to non-degeneracy assumptions), we must have

@@

Hence on the hyperplane $fp=g$, both the maximising index ${\bf{k}}^\ast(p)$ and the active index sets $\mathcal A_{\kappa_1}(p)$ 
and $\mathcal A_{\kappa_2}(p)$ must change, which implies that the problem is degenerate.
\item In order for a degenerate graph $\mathscr G(\mathcal W)$ to be parametrically convex, the vertices $v_{\kappa_1}(p)$ and $v_{\kappa_2}(p)$ must be identical for $fp\leq g$, and in particular their dependence on $p$ has to be identical.
This can be expressed using the implicit function theorem; thus

@@

implies

@@

  {\bf{a}}_{\mathcal J\cup \{u\}} \frac{dv_{\kappa}}{dp} &= {\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
and since we can assume that the inequalities are non-redundant for some right hand side, we find that 

@@

To complete the proof we note that~\eqref{eq:derivative:condition:on:index:sets} is a degenerate condition, in the sense that an arbitrarily small perturbation will result in $v_{\kappa_1}(p) \neq v_{\kappa_2}(p)$, and we therefore disregard this possibility.

@@

\vskip-1.15\baselineskip

@@

Corollary~\ref{thm:p:convexity:PWA:set:constant:num:verts} is essential for numerical evaluation since it can be reformulated as follows:
the set valued map defined by~\eqref{eq:definition:PWA:polytopic:set:general} is non-degenerate and parametrically convex iff 
it has a fixed number of vertices throughout the parameter space~$X$.

@@

In order to determine MRPI sets we need to be able to calculate the Pontryagin difference between point-to-set maps; hence we introduce the following.

@@

Let $\mathcal W: X\rightarrow\mathscr P(X)$ denote a point-to-set map, then the parametric Pontryagin difference $S \ominus \mathcal W(S)$ is convex for all convex sets $S$ if and only if $\mathcal W$ is parametrically convex.

@@

% \begin{thm}\label{thm:convexity:of:pontryagin:difference}
%   Let $S\subseteq X$ be a convex set and let $\mathcal W:X\rightarrow\mathscr P(X)$ be a parametrically convex point-to-set
%   map such that $\mathcal W(p)$ is convex for all $p\in X$, then $S\ominus \mathcal W(S)$ is convex.
% \end{thm}

@@

To prove convexity of $Z :=  S\ominus \mathcal W( S)$ when $\mathcal W$ is parametrically convex we pick any $z_1,z_2\in Z$, then
the definition of the parametric Pontryagin difference gives

@@

  \{z_i\} \oplus \mathcal W(z_i) \subseteq S,\; i=1,2 
and it can be verified that $ Z$ is convex by showing that line segments between all possible $z_1$ and $z_2$ are subsets of $Z$. In particular, for all $\lambda \in (0,1)$ we have

@@

 = &\lambda\underbrace{(\{z_1\}\oplus \mathcal W(z_1))}_{\subseteq S}\oplus
